\bf Eye Fitting Straight Lines in the Modern Era

### 2022-01-26 Eye-Fitting-Straight-Lines-in-the-Modern-Era.Rmd
edits to get supplementary material links to work.
proof reading and making edits.

Efforts in the field of statistical graphics have developed graphical testing tools and methods such as the lineup protocol [@buja2009statistical] to provide a framework for inferential testing.
Through experimentation, methods such as the lineup protocol allow researchers to conduct studies geared at understanding human ability to conduct tasks related to the perception of statistical charts such as differentiation, prediction, estimation, and extrapolation [@vanderplas2017clusters; @vanderplas2015spatial; @hofmann2012graphical].
One useful tool for testing statistical graphics is the concept of a lineup.
@buja2009statistical introduced the lineup protocol in which data plots are depicted and interpreted as statistics.
Supported by the grammar of graphics, a data plot can be characterized as a statistic, defined as, “a functional mapping of a variable or set of variables” [@vanderplas2020testing].
This allows the data plot to be tested similar to other statistics, by comparing the actual data plot
to a set of plots with the absence of any data structure we can test the likelihood of any perceived structure being significant.
The construction of data plots as statistics allow for easy experimentation, granting researchers the ability to compare the effectiveness of and understand the perception of different types of charts [@vanderplas2017clusters; @vanderplas2015spatial; @hofmann2012graphical].
The advancement of graphing software provides the tools necessary to develop new methods of testing statistical graphics.

@@

+ **Participant Data:** De-identified participant data collected in the study and used for analyses are available to be downloaded from GitHub [here](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data). 
+ **Data Analysis Code:** The code used to replicate the analysis in this paper can be found [here](https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html).
+ **Study Applet:** The shiny app used to conduct the study can be accessed [here](https://shiny.srvanderplas.com/you-draw-it/)

>>>>

One useful tool for testing statistical graphics is the concept of a lineup.
@buja2009statistical introduced the lineup protocol to provide a framework for inferential testing.
Through experimentation, methods such as the lineup protocol allow researchers to conduct studies geared at understanding human ability to conduct tasks related to the perception of statistical charts such as differentiation, prediction, estimation, and extrapolation [@vanderplas2017clusters; @vanderplas2015spatial; @hofmann2012graphical].
The advancement of graphing software provides the tools necessary to develop new methods of testing statistical graphics.

@@

+ **Participant Data:** De-identified participant data collected in the study and used for analyses are available to be downloaded from GitHub [here](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data). 
+ **Data Analysis Code:** The code used to replicate the analysis in this paper can be found [here](https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html).
+ **Study Applet:** The shiny app used to conduct the study can be accessed [here](https://shiny.srvanderplas.com/you-draw-it/).

### 2022-01-26 Eye-Fitting-Straight-Lines-in-the-Modern-Era.tex
edits to get supplementary material links to work.
proof reading and making edits.

Efforts in the field of statistical graphics have developed graphical
testing tools and methods such as the lineup protocol
\citep{buja2009statistical} to provide a framework for inferential
testing. Through experimentation, methods such as the lineup protocol
allow researchers to conduct studies geared at understanding human
ability to conduct tasks related to the perception of statistical charts
such as differentiation, prediction, estimation, and extrapolation
\citep{vanderplas2017clusters, vanderplas2015spatial, hofmann2012graphical}.
One useful tool for testing statistical graphics is the concept of a
lineup. \citet{buja2009statistical} introduced the lineup protocol in
which data plots are depicted and interpreted as statistics. Supported
by the grammar of graphics, a data plot can be characterized as a
statistic, defined as, ``a functional mapping of a variable or set of
variables'' \citep{vanderplas2020testing}. This allows the data plot to
be tested similar to other statistics, by comparing the actual data plot
to a set of plots with the absence of any data structure we can test the
likelihood of any perceived structure being significant. The
construction of data plots as statistics allow for easy experimentation,
granting researchers the ability to compare the effectiveness of and
understand the perception of different types of charts
\citep{vanderplas2017clusters, vanderplas2015spatial, hofmann2012graphical}.
The advancement of graphing software provides the tools necessary to
develop new methods of testing statistical graphics.

@@

\begin{itemize}
\tightlist
\item
  \textbf{Participant Data:} De-identified participant data collected in
  the study and used for analyses are available to be downloaded from
  GitHub
  \href{https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data}{here}.
\item
  \textbf{Data Analysis Code:} The code used to replicate the analysis
  in this paper can be found
  \href{https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html}{here}.
\item
  \textbf{Study Applet:} The shiny app used to conduct the study can be
  accessed \href{https://shiny.srvanderplas.com/you-draw-it/}{here}
\end{itemize}

>>>>

One useful tool for testing statistical graphics is the concept of a
lineup. \citet{buja2009statistical} introduced the lineup protocol to
provide a framework for inferential testing. Through experimentation,
methods such as the lineup protocol allow researchers to conduct studies
geared at understanding human ability to conduct tasks related to the
perception of statistical charts such as differentiation, prediction,
estimation, and extrapolation
\citep{vanderplas2017clusters, vanderplas2015spatial, hofmann2012graphical}.
The advancement of graphing software provides the tools necessary to
develop new methods of testing statistical graphics.

@@

\begin{itemize}
\tightlist
\item
  \textbf{Participant Data:} De-identified participant data collected in
  the study and used for analyses are available to be downloaded from
  GitHub
  \href{https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data}{here}.
\item
  \textbf{Data Analysis Code:} The code used to replicate the analysis
  in this paper can be found
  \href{https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html}{here}.
\item
  \textbf{Study Applet:} The shiny app used to conduct the study can be
  accessed \href{https://shiny.srvanderplas.com/you-draw-it/}{here}.
\end{itemize}
